Design and Implementation of Probabilistic Programming Language Anglican

### 2017-03-14 paper/paper.tex
input{toggle}, use make full or make ifl to switch
squeezed into 12 pages again

\newtoggle{full}
\input{toggle-ifl}

\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.85}\ttfamily\small, columns=flexible, showstringspaces=false}
}

@@

\begin{figure}
    \centering
    \includegraphics[trim={12pt 0 0 0},scale=0.6]{same-customer-time.pdf}
    \caption{Arrival time distribution for a single customer.}
    \label{fig:dist-same}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[trim={12pt 0 0 0},scale=0.6]{different-customers-times.pdf}
    \caption{Arrival time distributions for two customers.}
    \label{fig:dist-diff}
\end{figure}

@@

The macro \texttt{defdist} is used to define distributions.
\texttt{defdist} takes care of defining a separate type
for every distribution so that Clojure multimethods (or overloaded
methods) can be dispatched on
distribution types when needed, e.g. for custom proposal distributions 
used in an inference algorithm. The
Bernoulli distribution could be defined as follows:
\begin{lstlisting}[style=default]
(defdist bernoulli "Bernoulli distribution" [p]
  (sample* [this] (if (< (rand) p) 1 0))
  (observe* [this value]
    (Math/log (case value
                1 p
                0 (- 1. p)
                0.))))
\end{lstlisting}

>>>>

\newtoggle{full}
\input{toggle}

\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\iftoggle{full}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}
}{
\lstdefinestyle{default}{language=Anglican,basicstyle=\linespread{0.842}\ttfamily\small, columns=flexible, showstringspaces=false}
}

@@

\begin{figure}
    \centering
    \includegraphics[trim={6pt 12pt 0 12pt},scale=0.6]{same-customer-time.pdf}
    \caption{Arrival time distribution for a single customer.}
    \label{fig:dist-same}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[trim={6pt 12pt 0 12pt},clip,scale=0.6]{different-customers-times.pdf}
    \caption{Arrival time distributions for two customers.}
    \label{fig:dist-diff}
\end{figure}

@@

The macro \texttt{defdist} is used to define distributions.
\texttt{defdist} takes care of defining a separate type
for every distribution so that Clojure multimethods (or overloaded
methods) can be dispatched on
distribution types when needed, e.g. for custom proposal distributions 
used in an inference algorithm. The
Bernoulli distribution could be defined as follows:
\begin{lstlisting}[style=default]
(defdist bernoulli "Bernoulli distribution" [p]
  (sample* [this] (if (< (rand) p) 1 0))
  (observe* [this value]
    (Math/log (case value
                   1 p
                   0 (- 1. p)))))
\end{lstlisting}
